Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-03 paper/paper.tex
slightly adjusted Sendai supp figure legend to align with new labeling of figure
text for last section of Results

\figsupp[Validation of IFN reporter cell lines.]
{To validate the IFN reporter cell lines, they were infected at high MOI with the Cantell strain of Sendai virus, which strongly activates IFN expression~\citep{strahle2006sendai}.
At 13 hours post-infection, activation of the IFN reporter was then monitored by flow cytometry using the marker indicated at the bottom of each plot (either a fluorescent protein or antibody staining for the cell-surface LNGFR$\Delta$C using a PE-conjugated anti-LNGFR antibody from Miltenyi Biotec).
Sendai infection efficiently activated the IFN reporter in all cases, with the strongest signal from the IFN-$\lambda$ reporter driving ZsGreen.
}
{\includegraphics[width=0.5\textwidth]{figures/IFN_stochastic/IFN_reporter/Sendai_validation.pdf}}
\label{figsupp:reporter_validation}

@@

One other interesting trend emerges from the single-cell data.
There is no difference in the amount of viral mRNA between IFN+ and IFN- cells that express NS---but among cells that lack NS, the IFN+ ones have significantly more viral mRNA (\FIG{mutations}D).
The statistical analysis in \FIG{mutations}D is insufficient to determine if the higher viral transcriptional burden in IFN+ NS-deficient infections is a cause or a consequence of the IFN induction, but the experiments below shed more light on this question.

@@

\subsection{Distinct IFN-inducing characteristics of different viral variants}

@@

\jdbcomment{Section needs to be completed after remaining data on co-infections.}

@@

>>>>

\figsupp[Validation of IFN reporter cell lines.]
{To validate the IFN reporter cell lines, they were infected at high MOI with the Cantell strain of Sendai virus, which strongly activates IFN expression~\citep{strahle2006sendai}.
The name of each of reporter cell line is indicated at the top of each row of plots.
At 13 hours post-infection, activation of the IFN reporter was then monitored by flow cytometry using the marker indicated at the bottom of each plot (either a fluorescent protein or antibody staining for the cell-surface LNGFR$\Delta$C using a PE-conjugated anti-LNGFR antibody from Miltenyi Biotec).
Sendai infection efficiently activated the IFN reporter in all cases, with the strongest signal from the IFN-$\lambda$ reporter driving ZsGreen.
}
{\includegraphics[width=0.5\textwidth]{figures/IFN_stochastic/IFN_reporter/Sendai_validation.pdf}}
\label{figsupp:reporter_validation}

@@

One other interesting trend emerges from the single-cell data.
There is no difference in the amount of viral mRNA between IFN+ and IFN- cells that express NS---but among cells that lack NS, the IFN+ ones have significantly more viral mRNA (\FIG{mutations}D).
The statistical analysis in \FIG{mutations}D is insufficient to determine if the higher viral transcriptional burden in IFN+ NS-deficient infections is a cause or a consequence of IFN induction, but experiments below will shed more light on this question.

@@

\subsection{Distinct characteristics of IFN induction by different viral variants}

@@

The single-cell data reveal differences among IFN+ cells depending on the defect in the virion that infects them.
Specifically, \FIG{mutations}D shows that if a cell is infected by a virion that fails to express NS, then a higher viral transcriptional load correlates with IFN induction---but that no such association is present among infected cells that express NS.
To validate this conclusion, we used flow cytometry to compare the frequency of IFN induction among infected cells that express low or high levels of a viral protein (HA).
\FIG{mutantcomparison}A shows that upon infection with stocks of the NS1stop or NS1-A122V mutant, cells that express high levels of HA are much more likely to be IFN+ than those with low HA expression.
In contrast, if cells are infected with stocks of wildtype or PB1 amino-acid mutant virus, there is only a slight increase in IFN induction among cells with high HA expression.

To determine if higher viral transcriptional burden \emph{causes} IFN induction in NS-deficient infections, we treated infected cells with two different chemicals (ribavirin and cycloheximide) that inhibit secondary viral transcription, and so greatly reduce the level of viral transcripts~\citep{Vanderlinden:2016ec,Reuther:2015ef,Scholtissek:1976wg, killip2014activation}.
As shown in \FIG{mutantcomparison}A and \FIGSUPP[mutantcomparison]{cycloheximide}, both inhibitors markedly reduced IFN induction by cells infected with the NS1stop viral stock, but not by cells infected the virus carrying a deletion in PB1.
This result indicates that high levels of viral transcription promote IFN induction in NS-deficient infections, and suggests that there are distinct mechanisms of IFN induction by different viral variants---perhaps explaining why prior studies have not reached a consensus on the process by which influenza induces IFN~\citep{rehwinkel2010rig, weber2013incoming, killip2014activation}.

@@

\jdbcomment{It also confirms the suggestion by \citet{sjaastad2018distinct} that viral genetic variation contributes to the variability in gene expression among IFN+ cells.}
